Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2018-09-25 tex/older_tex/WW4C_VHzQ_20180913.tex
mainly MIR_LC updates

\subsubsection{Setup Matched Aperture Product}

To create matched aperture products it is first necessary to define the product. We do this in two requirements tables, \verb+RequiredMatchedApertureProduct+ and \verb+RequiredMapAverages+ that
tell the \textbf{ProgrammeBuilder} software which tables to create and what type of product is being created. These requirements tables also drive the pipeline.

\verb+RequiredMatchedApertureProduct+ contains the following attributes for the High-z QSO MAP product.
\begin{itemize}
    \item mapID, Identifier of the MAP product, value=1	
    \item archiveName, Main archive of product, value='VSA'/'WSA' 	
    \item programmeID, UID of programme, in this case a combined programme, value=10999
    \item extractor, Extractor used for forced photometry, value='CASU' (imcore_list)
    \item mapType, Type of MAP product (options 0 internal band-merged, 1 band-merged across surveys, 2 multi-epoch), value=2 
    \item name, Name of MAP product, value='highzQsoMap'
    \item description, Description of MAP product, 'Variability via matched apertures for set of high-z QSOs'	
    \item selection, Selection, e.g. File, pseudo-SQL, FITS image that is used to give input list, value='SELECTSTR qsoID,ra,dec FROMSTR finalQsoCatalogue'	
    \item finalProductTable, Name of final product table, value='highzQsoMapVariability'
    \item addSurveyList, List of additional archive/surveys that data comes from, value='NONE'
\end{itemize}

@@

\subsubsection{Selection of NIR variables}

To select potentially variable QSOs we first did a selection like Appendix D(??), selecting the photometry averaged over the whole time span to assess the overall signal-to-noise, total timespan and number of measurements. For each QSO in each filter measured by each instrument, our initial selection for potential variables was $N_{\rm meas}\geq8$, $T_{\rm tot}=\max{mjd}-\min{mjd}>30.$ days, $F>0.$ Jky and SNR>8, to give a signal-to-noise of $\sim\geq3$ per epoch and at least five measurements. An estimate was made of the number of useful epochs, such that $N_{\rm epc}=\min(N_{\rm meas},\frac{SNR}{sqrt{3.}}$. This in turn was used to estimate a typical time-scale for averaging, $T_{\rm avg}=\frac{T_{\rm tot}}{N_{\rm meas}}$.

We select average photometry where $(T_{\rm avg}/2.)\leq\verb+RequiredMapAverages.timeScale+\leq(2.*T_{\rm avg})$, a setup that should give the best combination of more epochs to resolve the variation and signal-to-noise per epoch. For each setup which satisfies this criteria, we get the averaged photometry and check the statistics. We calculate the median, and the median-absolute-deviation (MAD), and calculate the ratio of the standard deviation to the typical error, $r=\frac{1.48MAD}{ {\overline{error}/sqrt(N_{\rm epochs}}$. Likely variables have $rat\geq3.$ and $N_{\rm epoch}\geq4$. Using this selection, we found two potential variables, xx and yy, both of which show variability in VISTA, with timescales of xn and ym, respectively. [Put in results]

>>>>

\subsubsection{Setup Matched Aperture Product}
To create matched aperture products it is first necessary to define
the product. We do this in two requirements tables,
\verb+RequiredMatchedApertureProduct+ and \verb+RequiredMapAverages+
that tell the \textbf{ProgrammeBuilder} software which tables to
create and what type of product is being created. These requirements
tables also drive the pipeline.

\verb+RequiredMatchedApertureProduct+ contains the following attributes for the High-z QSO MAP product.
\begin{itemize}
    \item mapID, Identifier of the MAP product, value=1	
    \item archiveName, Main archive of product, value='VSA'/'WSA' 	
    \item programmeID, UID of programme, in this case a combined programme, value=10999
    \item extractor, Extractor used for forced photometry, value='CASU' (imcore\_list)
    \item mapType, Type of MAP product (options 0 internal band-merged, 1 band-merged across surveys, 2 multi-epoch), value=2 
    \item name, Name of MAP product, value='highzQsoMap'
    \item description, Description of MAP product, 'Variability via matched apertures for set of high-z QSOs'	
    \item selection, Selection, e.g. File, pseudo-SQL, FITS image that is used to give input list, value='SELECTSTR qsoID,ra,dec FROMSTR finalQsoCatalogue'	
    \item finalProductTable, Name of final product table, value='highzQsoMapVariability'
    \item addSurveyList, List of additional archive/surveys that data comes from, value='NONE'
\end{itemize}

@@

\subsubsection{Selection of NIR variables}
To select potentially variable QSOs we first did a selection like
Appendix D(??), selecting the photometry averaged over the whole time
span to assess the overall signal-to-noise, total timespan and number
of measurements. For each QSO in each filter measured by each
instrument, our initial selection for potential variables was $N_{\rm
meas}\geq8$, $T_{\rm tot}=\max{mjd}-\min{mjd}>30.$ days, $F>0.$ Jky
and SNR>8, to give a signal-to-noise of $\sim\geq3$ per epoch and at
least five measurements. An estimate was made of the number of useful
epochs, such that $N_{\rm epc}=\min(N_{\rm
meas},\frac{SNR}{sqrt{3.}}$. This in turn was used to estimate a
typical time-scale for averaging, $T_{\rm avg}=\frac{T_{\rm
tot}}{N_{\rm meas}}$.

We select average photometry where $(T_{\rm
avg}/2.)\leq\verb+RequiredMapAverages.timeScale+\leq(2.*T_{\rm avg})$,
a setup that should give the best combination of more epochs to
resolve the variation and signal-to-noise per epoch. For each setup
which satisfies this criteria, we get the averaged photometry and
check the statistics. We calculate the median, and the
median-absolute-deviation (MAD), and calculate the ratio of the
standard deviation to the typical error, 
$r=\frac{1.48MAD} {{\overline{error}/\sqrt(N_{\rm epochs})}}$. Likely variables have
$rat\geq3.$ and $N_{\rm epoch}\geq4$. Using this selection, we found
two potential variables, xx and yy, both of which show variability in
VISTA, with timescales of xn and ym, respectively. [Put in results]
